Block bootstrap consistency\\under weak assumptions

### 2016-09-19 Paper.tex
[#27] Make minor change in Lemma 1 proof
[#27] Add details to proof of Lemma 3

\subsection*{Proof of Theorem~\ref{T1}}
{%
\newcommand{\Db}[1][j]{D_{n#1}^{*}}
\newcommand{\Zsum}{\sum_{j=1}^{J_n} \Zb / \sigma_n}

@@

\begin{proof}
  For~\eqref{eq:25}, $(Z_{nj}^{*2} - \Em^* Z_{nj}^{*2}) \cdot (n /
  M_{nj})$ is a uniformly integrable martingale difference array, by
  Lemma~\ref{L6}, and
  satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
  For~\eqref{eq:26}, observe that
  \begin{align*}
    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big|
    &= \Big| \sum_{j=1}^{J_n} \big(Z_{nj}^{*} - \big[Z_{nj}^{*} + \tfrac{1}{\sqrt{n}} \sum_{t=K_{n,j-1}+1}^{K_{nj}} (\bar X_n - \mu_{nt}^*)\big]^2\big) \Big| \\
    &\leq 2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
    \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \Big)^{1/2}\\
    &\quad + \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
    (\mu_{nt}^{*} - \bar X_n)\Big)^2
  \end{align*}
  from the Cauchy-Schwarz inequality. Lemma~\ref{L5}, along
  with~\eqref{eq:17} and~\eqref{eq:25}, implies that
  $\sum_j Z_{nj}^{*2} = O_p(1)$. Lemma~\ref{L3} implies that
  \[
    \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \to^p 0
  \]
  since $\bar X$ itself obeys the \lln.

@@

\begin{proof}
  We will first show that, for every $\epsilon > 0$ and large enough
  $n$, there exists an $\epsilon' > 0$ with the property that
  \begin{equation}\label{eq:31}
    \E \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
  \end{equation}
  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn})$ with
  $\pr(A) \leq \epsilon'$. Then we will show that this property
  implies uniform integrability.\footnote{%
    The novelty in this part of the proof is the measurability
    requirement. The sigma-field $\Fs_n$ intentionally excludes the
    random variables that define the bootstrap (block length and block
    start periods) and any $A \in \Fs_n$ is independent of those
    variables, so $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measurable. If
    $\Fs_n$ were enlarged to include those variables then uniform
    integrability would be an immediate consequence of~\eqref{eq:31}
    and would not need to be shown separately. See \citet[Theorem
    12.9]{Dav:94}.} %

>>>>

\subsection*{Proof of Theorem~\ref{T1}}
{%
\newcommand{\Db}[1][j]{D_{n#1}^{*}}
\newcommand{\Zsum}{\sum_{j=1}^{J_n} \Zb / \sigma_n}
Observe that
\[
\sqrt{n}(\bar X_{n}^{*} -  \E^{*} \bar X_n^{*})
= \sqrt{n}((\bar{X}_{n}^{*} - \bar{\mu}_{n}^{*}) - \E^{*} (\bar X_n^{*} - \bar{\mu}_n^{*}))
+ \sqrt{n}(\bar{\mu}_{n}^{*} - \E^{*} \bar{\mu}_n^{*}).
\]
Lemma~\ref{L3} implies that the last term is $o_{L_2}(1)$, so we can assume that
$\mu_{nt}$ is constant in $t$ for each $n$ for the proof of normality. Convergence
in probability of the bootstrap variance and the bootstrap variance estimator
holds by Lemma~\ref{L4}.

@@

\begin{proof}
  For~\eqref{eq:25}, $(Z_{nj}^{*2} - \Em^* Z_{nj}^{*2}) \cdot (n /
  M_{nj})$ is a uniformly integrable martingale difference array, by
  Lemma~\ref{L6}, and
  satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
  For~\eqref{eq:26}, observe that
  \begin{multline*}
    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big|
    \leq 2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
    \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \Big)^{1/2} \\
    + \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
    (\mu_{nt}^{*} - \bar X_n)\Big)^2
  \end{multline*}
  from the Cauchy-Schwarz inequality. Lemma~\ref{L5}, along
  with~\eqref{eq:17} and~\eqref{eq:25}, implies that
  $\sum_j Z_{nj}^{*2} = O_p(1)$. Lemma~\ref{L3} implies that
  \[
    \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \to^p 0
  \]
  since $\bar X$ itself obeys the \lln.

@@

\begin{proof}
  We will first show that, for every $\epsilon > 0$ and large enough
  $n$, there exists an $\epsilon' > 0$ with the property that
  \begin{equation}\label{eq:31}
    \E \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
  \end{equation}
  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn})$ with
  $\pr(A) \leq \epsilon'$. Then we will show that this property
  implies uniform integrability.\footnote{%
    The novelty in this part of the proof is the measurability
    requirement. The sigma-field $\Fs_n$ intentionally excludes the
    random variables that define the bootstrap (block length and block
    start periods) and any $A \in \Fs_n$ is independent of those
    variables, so $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measurable. If
    $\Fs_n$ were enlarged to include those variables then uniform
    integrability would be an immediate consequence and would not need
    to be shown separately. See \citet[Theorem 12.9]{Dav:94}.} %
